\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Andrea Severi}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{seve-andre.github.io}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://seve-andre.github.io/}
\newcommand{\myLocation}{Cesena, IT }
\newcommand{\myPhoneNumber}{342-3209-388}
\newcommand{\yourEmail}{andrea.severi.dev@gmail.com}
\newcommand{\githubUserName}{seve-andre}
\newcommand{\linkedInUserName}{andrea-severi}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \myPhoneNumber
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{7pt}
    \normalsize \href{mailto:\yourEmail}{\underline{\yourEmail}} $|$
    \href{https://www.linkedin.com/in/andrea-severi/}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/seve-andre}{\underline{github/\githubUserName}} 
    $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
    \\ \vspace{3pt}
    \myLocation $|$ \myPhoneNumber
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{BS Computer Science and Engineering}{University of Bologna}{Cesena, IT}{Jul 2023}

% \teacherAssistant{World Wide Web Information Systems Development}
% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{\href{https://flashstart.com/}{Flashstart}}{Artificial Intelligence Intern}{Cesena, IT}{Jun 2022 – Jul 2022}
\begin{bullets}
    \item Conducted \textbf{web scraping} to retrieve website links datasets that correspond to specific categories.
    \item Performed \textbf{language detection} on the extracted text from the scraped websites.
    \item Utilized Python's NLTK to \textbf{remove stopwords} from the datasets.
    \item Applied \textbf{stemming and lemmatization} techniques through NLTK on the datasets to improve data quality.
    \item Created \textbf{word clouds} to visualize word frequency and importance in the datasets.
    \item Developed a \textbf{text classification neural network} using Keras and TensorFlow to categorize the data based on specific criteria.
\end{bullets}
\sectionsep

\resumeHeading{\href{https://flashstart.com/}{Flashstart}}{Artificial Intelligence Intern}{Cesena, IT}{Jul 2021 - Aug 2021}
\begin{bullets}
    \item Conducted vast research to retrieve datasets containing \textbf{foreign words to improve the accuracy} of the neural network.
    \item Utilized Python's NLTK to \textbf{remove stopwords} from the datasets, enhancing their quality and relevance.
    \item Applied \textbf{stemming and lemmatization} techniques through NLTK on the datasets to further refine the data.
    \item Developed a custom \textbf{translator to convert foreign language datasets to English}, enabling the neural network to analyze them more effectively.
    \item \textbf{Improved already-existing datasets} by conducting thorough quality checks, identifying and correcting errors and inconsistencies.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeadingWithDate{smart garden}{https://github.com/seve-andre/smart-garden}{C++, IoT, Arduino, Java}{Jul 2022}
Embedded \& IoT system implementing a simplified version of a smart garden, i.e., a smart system monitoring and controlling the state of the garden through sensors, HTTP protocol, serial and Bluetooth lines. \\
\sectionsep
  
\projectHeadingWithDate{myunibo}{https://github.com/seve-andre/myUniBo}{Kotlin, Jetpack Compose, Android}{May - Jun 2022}
Revisited \href{https://play.google.com/store/apps/details?id=com.myunibo}{myUniBo} University of Bologna app for students, that makes it simpler and more intuitive to book exams, see lessons of the day, grades and stats about student's career.
\sectionsep

\projectHeadingWithDate{airline traffic simulator}{https://github.com/seve-andre/OOP20-alt-sim}{Java, JavaFX}{May - Aug 2021}
Group project of a 2D desktop video game inspired by \href{https://www.youtube.com/watch?v=KTH084KeFBc}{Flight Control}. User's goal is to land as many airplanes as possible without causing collisions. Difficulty increases each time airplanes land, which makes you earn points.
\sectionsep

\projectHeadingWithDate{casine}{https://github.com/seve-andre/casine}{Tauri, Rust, Svelte, Typescript}{Feb - May 2023}
Apartment management system to stores guests, their data and info about owner's houses and apartments. Calculate final price, based on number of guests and their age. \\
\sectionsep

\projectHeadingWithDate{todoer}{https://github.com/seve-andre/todoer}{Kotlin, Jetpack Compose, Android}{Apr 2023}
Todoer is an Android app that helps users organize and manage their daily tasks by creating to-do lists and setting deadlines and reminders. Users can add, modify, or remove tasks from the list, organize them by priority, and more. \\
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, Kotlin, Python, Rust, TypeScript, SQL}
    \\
    \singleItem{Web Development:}{Svelte, Vue.js, PHP, JavaScript, TypeScript, HTML/CSS}
    \\
    \singleItem{Technology:}{Git, MySQL, SQLite, LaTeX}
\end{skillList}
\end{document}